A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-21 sections/queueing_model/waiting_time/main.tex
Change vocabulary in queueing section
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section
Add sentence to explain reason behind figures 4-6

Waiting time is the amount of time that individuals from either type wait in 
waiting zone 1 so that they can receive their service. 
For a given set of parameters there are three different performance measures 
around the mean waiting time that can be calculated. The mean waiting time of
type 1 individuals:

@@

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
The waiting times generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

>>>>

Waiting time is the amount of time that patients wait in 
the hospital's waiting space before they can receive their service. 
For a given set of parameters there are three different performance measures 
around the mean waiting time that can be calculated. The mean waiting time of
type 1 individuals:

@@

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the waiting time formula of
the constructed queueing model.
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
The waiting times generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.
